Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-15 automatica/paper.tex
address abate's comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We separate our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds a solution for more benchmarks (14) than the multi-staged back-end (13) \note{we should clarify that this is out of 26 in total, not 191?}.  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in terms of 
benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%
For the majority of the benchmarks with {\it floating-point} implementation, 
we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
but both back-ends find the same amount of solutions (13).  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

@@

\textcolor{blue}{Both approaches fail to synthesise a controller half of the instances.}  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

>>>>

We separate our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
(14) than the multi-staged back-end (13)}.
%\note{we should clarify that this is out of 26 in total, not 191?}  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in terms of 
benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%
For the majority of the benchmarks with {\it floating-point} implementation, 
we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
but both back-ends find the same amount of solutions (13).  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

@@

\textcolor{blue}{Both approaches fail to synthesise a controller for half of the instances.}  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.
